---
title: Advanced R Exercise Solution (2)
author: Xinchen Pan
date: '2018-05-21'
slug: advanced-r-exercise-solution-2
categories:
  - R
tags: 
  - R
---

##Functions

##Function Components

1. What function allows you to tell if an object is a function? What function allows you to tell if a function is a primitive function?

<strong>Answer:</strong>

<code>is.function</code>,<code>is.primitive</code>


```{r}
is.function(mean)
is.primitive(function(x) x ** 2)
```

2. This code makes a list of all functions in the base package.

```{r}
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)
```

Use it to answer the following questions:

a. Which base function has the most arguments?
```{r}
which.max(sapply(funs, function(x) length(formals(x))))
```

b. How many base functions have no arguments? What's special about those functions?


```{r}
length(names(funs)[sapply(funs, function(x) length(formals(x)) == 0)])
```

```{r}
length(names(funs)[sapply(funs, function(x) 
  {length(formals(x)) == 0 & is.primitive(x)})])
```
```{r}
names(funs)[sapply(funs, function(x) 
  {length(formals(x)) == 0 & !is.primitive(x)})]
```

Most of them are primitive functions.

c. 

```{r}
funs_primitive <- Filter(is.primitive, Filter(is.function, objs))
```

3. What are the three important components of a function?

<strong>Answer:</strong>

<ul><li>the <code>body()</code>, the code inside the function.</li>

<li>the <code>formals()</code>, the list of arguments which controls how you can call the function.</li>

<li>the <code>environment()</code>, the "map" of the location of the function's variables.
</li>
</ul>

4. When does printing a function not show what environment it was created in?

<strong>Answer:</strong>



```{r}
length(names(funs)[sapply(funs, function(x) is.null(environment(x)) | is.primitive(x))])
length(names(funs)[sapply(funs, function(x) is.null(environment(x)))])
length(names(funs)[sapply(funs, function(x) is.primitive(x))])
```

If the functions are primitive functions, printing them do not show the environment they were created in.


##Lexical scoping

1. What does the following code return? Why? What does each of the three c's mean?

```{r}
c <- 10
c(c = c)
```

The first c is the variable name. The <code>c = c</code> is to assign the first c which equals 10 to another c. The c outside the bracket is concatenation(<code>c()</code>.

2. What are the four principles that govern how R looks for values?

<ul> 
<li> name masking </li>
<li> Functions vs. variables </li>
<li>  A fresh start </li>
<li>  Dynamic lookup </li>
</ul>

3. What does the following function return? 

<strong>Answer:</strong>

202

```{r}
f <- function(x) {
  f <- function(x) {
    f <- function(x) {
      x ^ 2
    }
    f(x) + 1
  }
  f(x) * 2
}
f(10)
```

##Function arguments



1. Clarify the following list of odd function calls:

<strong>Answer:</strong>

```{r}
x <- sample(replace = TRUE, 20, x = c(1:10, NA))
y <- runif(min = 0, max = 1, 20)
cor(m = "k", y = y, u = "p", x = x)
```

In <code>sample()</code> and <code>runif()</code>, the order of the arguments does not matter as long as it is not ambiguous. 

In <code>cor()</code>, because of the lazy evaluation, <code>m = "k"</code> and <code>u = "p"</code> are not actually evaluated.

2. What does this function return? Why? Which principle does it illustrate?

<strong>Answer:</strong>

It returns 3.  

```{r}
f1 <- function(x = {y <- 1; 2}, y = 0) {
  x + y
}
f1()
```

If we check <code>{</code>, it shows <strong>For {, the result of the last expression evaluated. This has the visibility of the last evaluation.</strong>. Thus the function is equivalent to 

```{r}
f1 <- function(x = 2, y = 1) {
  x + y
}
f1()
```

The principle is lazy evaluation.

3. What does this function return? Why? Which principle does it illustrate?

<strong>Answer:</strong>

It returns 100. 

```{r}
f2 <- function(x = z) {
  z <- 100
  x
}
f2()
```

The principle it illustrates is <strong>dynamic lookup</strong>

##Special calls

1. Create a list of all the replacement functions found in the base package. Which ones are primitive functions?

<strong>Answer:</strong>

```{r}
names(funs)[sapply(names(funs), function(x) grepl("<-", x))]
```

2. 

What are valid names for user-created infix functions?

<strong>Answer:</strong>

It has to  start and end with %.

3. <strong>Answer:</strong>

```{r}
`%xor%` <- function(x, y){
  if(x != y)
    TRUE
  else 
    FALSE
}

F%xor%F
F%xor%T
T%xor%F
T%xor%T
```

4. Create infix versions of the set functions <code>intersect()</code>, <code>union()</code>, and <code>setdiff()</code>.


```{r}
(x <- c(sort(sample(1:20, 9)), NA))
(y <- c(sort(sample(3:23, 7)), NA))
```


<strong>Answer:</strong>

####infix version of intersect()
```{r}
`%ins%` <- function(x, y){
  result <- c()
  for(val in x){
    if(val %in% y){
      result <- c(val, result)
    }
  }
  if(is.null(result)){
    message("No common values")
  }
  else{
    unique(sort(result, na.last = TRUE))
  }
}

identical(intersect(x, y), x %ins% y)

c(1,2,3)%ins%c(1,2)
c(1,2,3)%ins%c(1,2,11,123)
c(1, 2)%ins%c(3, 4)
```

####infix version of union()

```{r}
`%union%` <- function(x, y){
  result <- y
  for(val in x){
      result <- c(val, result)
  }
  unique(sort(result, na.last = TRUE))
}

setdiff(x %union% y,  union(x, y))

c(6, 3, 2, 4) %union% c(2, 5, 8)
c(6, 3, 2, 4) %union% c(4, 0, 1)
```

####infix version of union()

```{r}
`%setdiff%` <- function(x, y){
  result <- c()
  for(val in x){
    if(!(val %in% y)){
      result <- c(val, result)
    }
  }
    unique(sort(result, na.last = TRUE))
}

identical(x %setdiff% y, setdiff(x, y))
```

5. Create a replacement function that modifies a random location in a vector.

<strong>Answer:</strong>

```{r}
x <- 1:10
`modify<-` <- function(x, value) {
  x[sample(length(x), 1)] <- value
  x
}
modify(x) <- 6324
x
```


##Return values

How does the chdir parameter of source() compare to in_dir()? Why might you prefer one approach to the other?

<strong>Answer:</strong>

```{r, eval=FALSE}
##The chdir parameter of source()

if (chdir) {
            if (is.character(ofile)) {
                if (grepl("^(ftp|http|file)://", ofile)) 
                  warning("'chdir = TRUE' makes no sense for a URL")
                else if ((path <- dirname(ofile)) != ".") {
                  owd <- getwd()
                  if (is.null(owd)) 
                    stop("cannot 'chdir' as current directory is unknown")
                  on.exit(setwd(owd), add = TRUE)
                  setwd(path)
                }
            }
            else {
                warning
            }
  
in_dir <- function(dir, code) {
  old <- setwd(dir)
  on.exit(setwd(old))

  force(code)
}
```

If we set <code>chdir = TRUE</code>, the working directory is temporarily changed from <code>getwd()</code> to where the sourced file locates. <code>in_dir</code> is more flexible, we can change the directory to anywhere we want temporarily.


2. What function undoes the action of <code>library()</code>? How do you save and restore the values of <code>options()</code> and <code>par()</code>?

<strong>Answer:</strong>

Use <code>detach()</code>

```{r,}
library(ggplot2)
detach(package:ggplot2)
```

Just use <code>options()</code>

tbc
