---
title: Advanced R Exercise Solution (5)
author: Xinchen Pan
date: '2018-06-13'
slug: advanced-r-solution-5
categories:
  - R
tags: []
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Debugging, condition handling, and defensive programming

###Condition handling

1. Compare the following two implementations of <code>message2error()</code>. What is the main advantage of  <code>withCallingHandlers()</code> in this scenario? (Hint: look carefully at the traceback.)

```{r}
message2error <- function(code) {
  withCallingHandlers(code, message = function(e) stop(e))
}
message2error1 <- function(code) {
  tryCatch(code, message = function(e) stop(e))
}
```

### Defensive programming 

1. The goal of the <code>col_means()</code> function defined below is to compute the means of all numeric columns in a data frame.

```{r}
col_means <- function(df) {
  numeric <- sapply(df, is.numeric)
  numeric_cols <- df[, numeric]

  data.frame(lapply(numeric_cols, mean))
}
```

However, the function is not robust to unusual inputs. Look at the following results, decide which ones are incorrect, and modify <code>col_means()</code> to be more robust. (Hint: there are two function calls in <code>col_means()</code> that are particularly prone to problems.)


```{r}
#correct
col_means(mtcars)
```

```{r, eval=FALSE}
col_means(mtcars[, 0])
#Error in .subset(x, j) : invalid subscript type 'list'
```
```{r, eval=FALSE}
mtcars[0, ]
```

```{r,eval=FALSE}
col_means(1:10)
#Error in df[, numeric] : incorrect number of dimensions
```


```{r}
#This calculates the row mean
col_means(mtcars[, "mpg", drop = F])
```


```{r, eval=FALSE}
col_means(as.matrix(mtcars))
#Error in df[, numeric] : (subscript) logical subscript too long
```


```{r, eval=FALSE}
col_means(as.list(mtcars))
#Error in df[, numeric] : incorrect number of dimensions
```

```{r}
#
mtcars2 <- mtcars
mtcars2[-1] <- lapply(mtcars2[-1], as.character)
col_means(mtcars2)
```

<strong>Revised <code>col_means</code></strong>
```{r}
col_means2 <- function(df) {
  df <- data.frame(df)
  numeric <- vapply(df, is.numeric, logical(1))
  numeric_cols <- df[, numeric, drop = FALSE]

  data.frame(lapply(numeric_cols, mean))
}
```


```{r}
col_means2(mtcars)
col_means2(mtcars[, 0])
col_means2(mtcars[0, ])
col_means2(mtcars[, "mpg", drop = F])
col_means2(1:10)
col_means2(as.matrix(mtcars))
col_means2(as.list(mtcars))

mtcars2 <- mtcars
mtcars2[-1] <- lapply(mtcars2[-1], as.character)
col_means2(mtcars2)
```

2. The following function “lags” a vector, returning a version of x that is n values behind the original. Improve the function so that it (1) returns a useful error message if n is not a vector, and (2) has reasonable behaviour when n is 0 or longer than x.

```{r}
lag <- function(x, n = 1L) {
  if (!is.vector(x)){
    stop("x needs to be a vector ")
  } else{
  xlen <- length(x)
  }
  if (n > xlen){
    c(rep(NA, xlen))
  } else{
    c(rep(NA, n), x[seq_len(xlen - n)])
  }
  
}
```

```{r}
lag(1:10, 1)
lag(1:10, 100)

