---
title: Advanced R Exercise Solution (3)
author: Xinchen Pan
date: '2018-06-08'
slug: advanced-r-exercise-solution-3
categories:
  - R
tags:
  - R
---

```{r, echo=FALSE}
library(pryr)
```

The exercise is getting harder.

## OO field guide

### Base types & S3 

1. Read the source code for <code>t()</code> and <code>t.test()</code> and confirm that <code>t.test()</code> is an S3 generic and not an S3 method. What happens if you create an object with class test and call <code>t()</code> with it?

```{r}
t
t.test
```

```{r}
ftype(t)
ftype(t.test)
```

Since object test does not have a method <code>t()</code> associated with it. Calling <code>t()</code> will call the default class. 

2.  What classes have a method for the Math group generic in base R? Read the source code. How do the methods work?


```{r}
methods(Math)
```

3.  R has two classes for representing date time data, <code>POSIXct</code> and <code>POSIXlt</code>, which both inherit from <code>POSIXt</code>. Which generics have different behaviours for the two classes? Which generics share the same behaviour?

Basically the generics of those two inherited classes that exist in <code>POSIXct</code> share the same behavior. The generics that only exist in one class has different behavior. 

```{r}
methods(class = "POSIXt")
```


```{r}
methods(class="POSIXct")
```

```{r}
methods(class="POSIXlt")
```

4. Which base generic has the greatest number of defined methods?

```{r}
library(pryr)
objs <- mget(ls("package:base"), inherits = TRUE)
funs <- Filter(is.function, objs)

generics <- funs[sapply(funs, function(x) ("generic" %in% ftype(x)))]

names(generics)[which.max(sapply(names(generics), function(x) length(methods(x))))]
```

5. <code>UseMethod()</code> calls methods in a special way. Predict what the following code will return, then run it and read the help for <code>UseMethod()</code> to figure out what’s going on. Write down the rules in the simplest form possible.


```{r}
y <- 1
g <- function(x) {
  y <- 2
  UseMethod("g")
}
g.numeric <- function(x) y
g(10)

h <- function(x) {
  x <- 10
  UseMethod("h")
}
h.character <- function(x) paste("char", x)
h.numeric <- function(x) paste("num", x)

h("a")
```

<code>g(10)</code> will return 2. Since y is not in the function, it will search in <code>g</code>

<code>h("a")</code> will return "char a" because "a" is a character. <code>h.numeric()</code> will not be executed or further searched.

6. Internal generics don’t dispatch on the implicit class of base types. Carefully read <code>?"internal generic"</code> to determine why the length of f and g is different in the example below. What function helps distinguish between the behaviour of <code>f</code> and <code>g</code>?


```{r}
f <- function() 1
g <- function() 2
class(g) <- "function"

class(f)
class(g)

length.function <- function(x) "function"
length(f)
length(g)
```

<code>length(f)</code> will not search for <code>length.function</code> thus "function" will not be returned unlike <code>length(d)</code>. <code>f</code> does not have a class associated with it so internal generics don’t dispatch on the implicit class of base types. 



###S4

1. Which S4 generic has the most methods defined for it? Which S4 class has the most methods associated with it?

```{r}
generics<- getGenerics(where = search())
generics_s4 <- generics@.Data[sapply(generics@.Data, function(x) isS4(get(x)))]

generics_s4[which.max(sapply(generics_s4, function(x) length(methods(x))))]
```


```{r}
s4class <- getClasses(where = .GlobalEnv, inherits = TRUE)

Methods <- sapply(s4class, function(x) showMethods(classes = x, printTo = FALSE))

names(Methods)[which.max(lapply(Methods, function(x) length(grep("Function", x))))]
```

2. What happens if you define a new S4 class that doesn’t “contain” an existing class? (Hint: read about virtual classes in <code>?setClass</code>.)

<blockquote>
In the latter case, a virtual class may include slots to provide some common behavior without fully defining the object—see the class traceable for an example. Note that "VIRTUAL" does not carry over to subclasses; a class that contains a virtual class is not itself automatically virtual.
</blockquote>



3. What happens if you pass an S4 object to an S3 generic? What happens if you pass an S3 object to an S4 generic? (Hint: read <code>?setOldClass</code> for the second case.)


###RC

1. Use a field function to prevent the account balance from being directly manipulated. (Hint: create a “hidden” .balance field, and read the help for the fields argument in <code>setRefClass()</code>.)

Not sure

2. I claimed that there aren’t any RC classes in base R, but that was a bit of a simplification. Use <code>getClasses()</code> and find which classes <code>extend()</code> from <code>envRefClass</code>. What are the classes used for? (Hint: recall how to look up the documentation for a class.)

```{r}
classes <- getClasses(where = .GlobalEnv, inherits = TRUE)

classes[(sapply(classes, function(x) extends(x, "envRefClass")))]
```




